DNSKEY Management

### 2012-12-09 paper/paper.tex
first conclusion try...

>>>>

\section{Conclusion\wbjp\wbts}
%TODO improve conclusion... :-D
We have exposed the administrative challenges that arise with DNSSEC: while being far from trivial, these issues are not insurmountable, especially with regard to the gained benefits, and the modifications required from the three R's to their interaction process finally only consists in adaptations to already existing communication channels.

From this point of view, DNSSEC's requirements and goals seem to be reachable.

SWITCH's case study showed that the existing issues can at least be harnessed at a TLD level. While a wider adoption is required to see if the infrastructure can indeed scale, the foundations that have been lain seem ready to take on the challenge.
